\documentclass[11pt,letterpaper,rotate]{article}

\pagestyle{plain}

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{longtable}

% remove the next section in the final version
%\usepackage[paperwidth=275.9mm, paperheight=279.4mm]{geometry} % regular letter size is 215.9 wide by 279.44 long
%\setlength{\evensidemargin}{95mm}
\usepackage[colorinlistoftodos, textwidth=65mm, shadow]{todonotes}

\newcounter{todocounter}
\newcommand{\todonum}[2][]{\stepcounter{todocounter}\todo[#1]{\thetodocounter: #2}}


\title{Vision and Scope Document \\
for \\
APO Theta Upsilon Chapter Website\\
Devin Schwab\\
Jonathan Chan}
\date{September 21, 2012}

\begin{document}

\maketitle
\newpage

\tableofcontents


\newpage

\section{Business Requirements}

\subsection{Background, Business Opportunities, Customer Needs}

\indent\indent Alpha Phi Omega is a national service fraternity. The
fraternity is co-ed and the major focus is on providing service to the
country, the community, the campus and the chapter. APO chapters also
include a number of social events known as fellowship events. Most chapters keep track of data such as service hours completed by each member via paper documents. However, as chapter sizes grow the paper method becomes unwiedly. Case's Theta Upsilon chapter currently has 91 active members and a total of over 145 people with some involvement. There is clearly a need for a robust and easy to use system to manage not only service hour tracking but other aspects of the chapter's administration.

Case's Theta Upsilon chapter currently has a website located at \\
http://apo.case.edu. However, this website is currently only useful for
tracking service hours and membership requirements. This tracking functionality is very rudimentary. In addition, the code running behind the website has been developed using a build-and-fix model leading to a mix of coding styles, no documentation, difficult to track down bugs and a very difficult codebase to add new features to. As the chapter has grown it has become desirable to add more administrative features as well as social features for the brothers to connect with. Adding these features on top of the current code base would be difficult and lead to unstable code. This leads us to believe there is an opportunity to make a new website. One that is documented, provides more administrative tools, is designed with future improvements in mind and is overall easier for all parties involved to use.


\subsection{Business Objectives and Success Criteria}
\FloatBarrier
\begin{longtable}{lp{12cm}}
{\bf BO-1} & Reduce amount of time to sign-up, report, and track a
service event by at least 25\% by half a semester from release date \\
{\bf BO-2} & Reduce amount of time chapter officers must spend on the
paperwork and administration part of their duties by 25\% by half a
semester from release date \\
{\bf BO-3} & Reduce amount of support emails to webmaster by 25\% after
half a semester of use \\
\end{longtable}

\FloatBarrier
\begin{longtable}{lp{12cm}}
{\bf SC-1} & Amount of visits per week to website for each chapter member
increases to 4 or more times per week. \\
{\bf SC-2} & Majority of members find website 'satisfactory' or better
when surveyed
within one semester of release\\
\end{longtable}

\FloatBarrier

\subsection{Business Risks}

\FloatBarrier
\begin{longtable}{lp{12cm}}
{\bf RI-1} & Data might be lost in transition from old website to new
website \\
{\bf RI-2} & Enough users may not use the new features to make them useful
for those who are using them (also known as network effect) \\
\end{longtable}

\section{Vision of the Solution}

\subsection{Vision Statement}

\indent\indent For general members of the chapter the website will be a place to report what type of community service they have done and how many hours they have completed. In addition, the members of the chapter will be able to check-in on the status of the chapter including upcoming events and important deadlines. The website will also act as a way for brothers to find out more about one another and get in contact with each other for bonding outside of chapter events.

For the members in charge of the chapter's administration, the website will also serve as a tool for accomplishing their jobs. These jobs include things such as budgeting, service hour approval, fellowship planning, and contract review. The tools will be well documented so that members who have not previously held a position will be able to quickly get up to speed.

For those outside of the chapter the website will serve as a source of information about both Case's chapter and the national fraternity. It will provide specific information about how to join and why one would want to join. This will help in recruiting new members.

\subsection{Major Features}

\begin{longtable}{lp{12cm}}
{\bf FE-1:} & Create, update, track, and report service events and
hours \\
{\bf FE-2:} &Create, update, sign, and track progress of member
contracts \\
{\bf FE-3: } &Create, update, and view member profiles\\
{\bf FE-4: } &Update and view chapter calendar\\
{\bf FE-5: } &Write and comment on chapter blog\\
{\bf FE-6: } &Photo integration\\
{\bf FE-7: } &Create and update Alumni database\\
{\bf FE-8: } &Chapter statistics tracking and reporting\\
\end{longtable}


\subsection{Assumptions and Dependencies}

\begin{longtable}{lp{12cm}}
{\bf AS-1:} & Members all have access to a computer and an internet
connection\\
{\bf AS-2:} & Members all have Case IDs\\
\end{longtable}

\begin{longtable}{lp{12cm}}
{\bf DE-1:} & The website depends on free web hosting\\
{\bf DE-2:} & The website will be provided with a free domain name\\
\end{longtable}

\section{Scope and Limitations}

\subsection{Scope of Initial and Subsequent Releases}

\begin{longtable}{|l|p{4cm}|p{4cm}|p{4cm}|}
\hline
{\bf Feature} & {\bf Version 0.0} & {\bf Version 0.5} & {\bf Version 1.0} \\
\hline
{\bf FE-1} & Fully Implemented & ~ & ~ \\ \hline
{\bf FE-2} & Fully Implemented & ~ & ~ \\ \hline
{\bf FE-3} & Login Implemented & Fully Implemented & ~ \\ \hline
{\bf FE-4} & Fully Implemented & ~ & ~ \\ \hline
{\bf FE-5} & Not Implemented & Fully Implemented & ~ \\ \hline
{\bf FE-6} & Not Implemented & Not Implemented & Fully Implemented \\
\hline
{\bf FE-7} & Not Implemented & Fully Implemented & ~ \\ \hline
{\bf FE-8} & Not Implemented & Not Implemented & Fully Implemented \\ \hline
\end{longtable}

\subsection{Limitations and Exclusions}

\begin{longtable}{lp{12cm}}
{\bf LI-1:} & Administrative features of the website will only be
available to officers of the chapter\\
{\bf LI-2:} & The full feature set for event tracking and
administration will only be avilable for events run and operated by
the chapter\\
\end{longtable}
\newpage

\section{Business Contexts}

\subsection{Stakeholder Profiles}

\FloatBarrier
\begin{flushleft}
    \begin{longtable}{@{}|p{2.2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
        \hline
        {\bf Stakeholder}        & {\bf Major Value}
        & {\bf Attitude}
        & {\bf Major Interests}
        & {\bf Constraints}                                      \\ \hline
        {\bf Exec}               & Improved ease of updating website, better communication with the entire chapter           & Very committed to the fraternity, enthusiastic to help in any way possible & Brother retention, attracting new brothers and pledges, organizing events & Website must be easy to understand how to update \\ \hline
        {\bf Brothers}           & Improved communication and access to events, more organized and accessible event sign ups & Most will be willing to help, looking forward to a more modern website     & Doing service events, PR events, fellowship events, signing contracts     & None identified                                  \\ \hline
        {\bf Pledges}            & Better representation of the fraternity, better access to events                          & Will enjoy the ease of use.                                                & Doing service events, PR events, fellowship events, signing contracts     & None identified                                  \\ \hline
        {\bf Interested Parties} & Better representation of the fraternity                                                   & Possibly the first impression of the fraternity                            & Finding information about the fraternity                                  & None identified                                  \\
        \hline

\end{longtable}
\end{flushleft}
\FloatBarrier

\newpage
\subsection{Project Priorities}

\FloatBarrier

\begin{flushleft}
\begin{longtable}{@{}|p{2.7cm}|p{3.7cm}|p{3.7cm}|p{3.7cm}|}
        \hline
        {\bf Dimension} & {\bf Driver}                   & {\bf
          Constraint}
        & {\bf Degree of Freedom}                    \\ \hline
        {\bf Schedule}  & ~                        & ~
        & Version 1.0 completed by December 7th 2012 \\ \hline
        {\bf Features}  & ~                        & Any feature scheduled in this document must be complete and fully operational for version 1.0 & ~                                    \\ \hline
        {\bf Quality}   & ~                        & All security
        tests must pass, all exec members must be able to use without
        issue, must not lose any features of the current website      & ~                                    \\ \hline
        {\bf Staff}     & Two part time developers & ~                                                                                     & ~                                    \\ \hline
        {\bf Cost}      & ~                        & ~                                                                                     & None projected                       \\
        \hline
\end{longtable}
\end{flushleft}
\FloatBarrier

\end{document}
