\documentclass{article}

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{fancyhdr}
\usepackage{longtable}
\usepackage{lastpage}
\usepackage{rotating}
\usepackage{pdfpages}
\usepackage[hidelinks]{hyperref}

% clear the default headers
\fancyhead{}
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand{\projName}{APO Chapter Organization Website}
\newcommand{\docName}{Software Design Document}
\newcommand{\docVersion}{Version 1.0}
\newcommand{\docDate}{October 10, 2012}

\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\setlength\LTleft{0pt}
\setlength\LTright{0pt}

\fancypagestyle{plain}{

\headheight=10mm
\fancyhead{\begin{longtable}{@{\extracolsep{\fill}}|l|r|}
\hline
\projName & \docVersion \\ \hline
\docName & \docDate \\ \hline
\end{longtable}}

\fancyfoot[C]{\footnotesize Page \thepage\ of \pageref{LastPage}}}

\pagestyle{plain}

\setcounter{tocdepth}{2}

\title{\projName \\ \vspace{10 mm}
\docName \\ \vspace{10 mm}
Devin Schwab\\
Jon Chan}

\date{\docDate}

\begin{document}
\bibliographystyle{IEEE}

\maketitle

\newpage

\begin{longtable}{|l|l|l|l|}
\hline
{\bf Date} & {\bf Version} & {\bf Description} & {\bf Authors} \\ \hline
10/8/12 & Version 0.5 & Initial Draft & Devin Schwab, Jon Chan \\ \hline
\end{longtable}

\newpage

\tableofcontents
\listoffigures

\newpage

\section{Introduction}

\subsection{Document Overview}
The \projName is a new website designed to replace the existing website.
The current website provides basic administrative features for some of the executive positions.
It also provides some basic features that allow brothers to keep in touch. However, each semester
more features are requested and the current website was not designed with future maintainability
in mind. For this reason this project seeks to make a new website that will provide better
administrative tools and better social tools. The goal is for the website to decrease the amount of effort
needed for administration and to get chapter members more involved in the organization. This document lays out
the design for the new website including the overall architecture, rationale for selected components and
services and the specifications of new components and services which must be created.

\subsection{Document Conventions}
This document references previous documents created for this project as well as documentation
for outside systems this system will interact with. References for the system can be found at the end of the document.
In text citations are listed as numbers in square brackets. For example ``[ 1 ]''. 

\subsection{Definitions and Acronyms}

% Add definition to the table
\begin{tabular}{p{.20\textwidth}p{.80\textwidth}}

\multicolumn{2}{c}{ {\bf Definitions} } \\ \hline
{\bf Brother} & A general member of the chapter that has gone through the pledging process. \\ \hline
{\bf Contract} & The requirements that a member must satisfy to remain in good standing with the chapter \\ \hline
{\bf Exec Member} & A general member of the chapter (brother) that is elected or appointed to run a specific aspect of the chapter. \\ \hline
{\bf Membership Review} & Event at the end of the semester in which the completion of each member's contract is reviewed by the chapter\\ \hline
{\bf Pledge} & A member who has completed the initiation ceremony, but not the induction ceremony. These members do not have the full privilege of a brother\\ \hline
{\bf Rushee} & A person who is interested in joining APO, but is not yet a pledge \\ \hline
{\bf Service Report} & Request for approval of community service hours\\ \hline
{\bf Alumni} & A person who was previously a member, but has since graduated\\ \hline
\end{tabular}

\begin{tabular}{p{.20\textwidth}p{.80\textwidth}}
\multicolumn{2}{c}{ {\bf Acronyms} } \\ \hline
GAE & Google App Engine \\ \hline
SSL & Secure Socket Layer \\ \hline
\end{tabular}

\section{Design Overview}

\subsection{Architecture}

The basic architecture follows a design pattern for the website.

{\bf INSERT GENERAL ARCHITECTURE DIAGRAM}

Multiple users connect to a webserver running our software and database via the Internet.
Setting up a webserver also requires setting up a Domain Name System (DNS) server and registering a domain
name.

The following subsections detail design decisions for each aspect of this general architecture.

In order to simplify the setup, maintenance and cost of operations for the website Google App Engine (GAE) shall be used.
The choice of GAE restricts the database to Google's Big Table datastore.

One of the features of the website requires 
the storage of user submitted photos. While the photos could be stored on the server provided by GAE, GAE provides a
limited amount of storage space. If users want to upload high resolution photos the server will quickly run out of the 
free storage. To mitigate this the website will use an outside photo site as a place to store and organize the photo.
The website will simply act as a user interface to the storage sight. The chapter currently uses Photobucket for the photos
meaning many photos are already uploaded there. In addition Photobucket has very large storage limits {\bf FILL IN STORAGE LIMIT AND GIVE A CITATION TO THE WEBSITE}. For this reason Photobucket will be used for storing the photos.

Based on these design decisions the website architecture is as follows

{\bf INSERT WEBSITE ARCHITECTURE DIAGRAM}


\subsection{Webserver - Google App Engine}

One necessary part of the architecture is the webserver which will run the actual application. There are two main options
for the webserver: buy a computer and configure it to be a webserver or use a hosting service. In the vision and scope document for this project
one of the assumptions was that the website will be hosted for free and that the website will be provided with a free
domain name. \cite{schwab_apo_2012} This rules out the buy and configure a webserver option. So it is necessary to select a free hosting service.

There are a multitude of free hosting services on the web, but the services vary in quality and not all packages
come with a free domain name. The free services are often limited in the amount of bandwidth and storage they can use.
Out of the surveyed hosting services with free packages Amazon EC2 offered the most amount of free bandwidth and storage. \cite{amazon_amazon_2012} \cite{heroku_heroku_2012} \cite{google_quotas_2012} However, using Amazon EC2 would require setup and configuration of a webserver and database server. In addition Amazon EC2's free tier is only free for the first year. After which the user must pay for all services.

On the other hand Google App Engine (GAE) has a free tier that does not expire. The amount of resources provided for free are not as high as Amazon's free tier, but the service will remain free for the foreseeable future.  \cite{google_quotas_2012} In addition GAE provides a free hostname by giving the application a subdomain of the appspot.com domain.
An additional benefit of GAE is that the free domain also comes with a free Secure Socket Layer (SSL) Certificate. An SSL 
certificate will be needed to provide secure login pages and to encrypt and authenticate sensitive information.

\subsection{Database - Google's Bigtable Datastore}

\subsection{Application Language - Flask and Python}

\subsection{Photo Storage - Photobucket}

\section{Component Specification}

\newpage

\bibliography{designBib}

\end{document}